### 2018-11-27 pilot_manuscript.Rmd
updated pilot stuff

```{r load_packages, include = FALSE}
library(papaja) 
library(MuMIn)
library(reshape)
library(nlme)
library(ggplot2)
library(expss)

@@

@Warriner2014 *WE NEED THIS IN MENDELEY* utilized the new affective norms list in order to investigate the validity of the Pollyanna hypothesis, or the prevalence of a generally optimistic outlook in humans as reflected in langauge. The researchers were able to conclude the existence of a greater number of positive-valence English words in the list of 13,915 lemmas. Additionally, after observing token frequency in a number of text corpora, including SUBTLEX-US, COCA, BNC, TASA, and HAL, the researchers found that words with postive valence were also used more frequently [@Warriner2014]. While the researchers concede the possiblility of an acquiensence bias in ratings as a possible explanation for the observed positivity bias, this investigation represents one application of the @Warriner2013 list in emotional studies.

One cognition-based study investigates the relationship between emotion and response latencies in word recognition. @Kuperman2014 *WE NEED THIS IN MENDELEY* sought to use the @Warriner2013 norms to fill in the knowledge gaps regarding variance in word recognition. The researchers drew several conclusions regarding emotion and word recognition (specifically in naming and lexical decision tasks). First, @Kuperman2014 found higher response latencies in negative-valence words, lower response latencies in neutral words, and even lower response latencies in words with positive valence. The researchers also concluded that words causing higher arousal tend to have higher response latencies than less-arousing words. They found valence had a stronger effect on recognition than arousal (both effects were independent, not interactive). They found an interaction between emotion and word frequency such that valence and arousal are more effective on lower frequency words than high frequency words. Finally, @Kuperman2014 found a greater effect for lexical decision tasks than for naming tasks. This research serves as further evidence that the @Warriner2014 list can be used for research inquiries both within and without the field of psycholinguistics.

@@

# Method - Experiment 1

@@

Once the MFD was separated along lines of positive and negative dimensions for each of the foundations, the article text was processed using the *tm* and *ngram* packages in *R* in order to render the text in lowercase, remove punctuation, and fix spacing issues [@CITE_tm]. The individual words were then reduced to their stems (i.e., *abused* was stemmed to *abus*). The same procedure was applied to the MFD words, and the addition of multiple forms of each concept allowed for the capture of all versions of stemming that might occur given *tm*'s English stemmer function. The source article words were compiled into a dataset where they were matched up with their counterparts in the MFD along with a percentage of their occurrence. Therefore, for each article, the percentage of the number of *harm* (low end) and *care* (high end) related words were calculated and this process was repeated for each of the foundations. This procedure created ten percentages that were included as the dependent variable for the following analyses.

```{r stem_text, eval=TRUE, include=FALSE}

@@

# Experiment 1 results

@@

# Method - Experiment 2

@@

@@

@@

## Experiment 1

## Experiment 2

## General discussion
How it turned out

>>>>

```{r load_packages, include = FALSE}
library(papaja) 
library(MuMIn)
library(reshape)
library(nlme)
library(ggplot2)
library(expss)
library(MOTE)

@@

@Warriner2014 utilized the new affective norms list in order to investigate the validity of the Pollyanna hypothesis, or the prevalence of a generally optimistic outlook in humans as reflected in langauge. The researchers were able to conclude the existence of a greater number of positive-valence English words in the list of 13,915 lemmas. Additionally, after observing token frequency in a number of text corpora, including SUBTLEX-US, COCA, BNC, TASA, and HAL, the researchers found that words with postive valence were also used more frequently [@Warriner2014]. While the researchers concede the possiblility of an acquiensence bias in ratings as a possible explanation for the observed positivity bias, this investigation represents one application of the @Warriner2013 list in emotional studies.

One cognition-based study investigates the relationship between emotion and response latencies in word recognition. @Kuperman2014 sought to use the @Warriner2013 norms to fill in the knowledge gaps regarding variance in word recognition. The researchers drew several conclusions regarding emotion and word recognition (specifically in naming and lexical decision tasks). First, @Kuperman2014 found higher response latencies in negative-valence words, lower response latencies in neutral words, and even lower response latencies in words with positive valence. The researchers also concluded that words causing higher arousal tend to have higher response latencies than less-arousing words. They found valence had a stronger effect on recognition than arousal (both effects were independent, not interactive). They found an interaction between emotion and word frequency such that valence and arousal are more effective on lower frequency words than high frequency words. Finally, @Kuperman2014 found a greater effect for lexical decision tasks than for naming tasks. This research serves as further evidence that the @Warriner2014 list can be used for research inquiries both within and without the field of psycholinguistics.

@@

# Experiment 1

# Method

@@

Once the MFD was separated along lines of positive and negative dimensions for each of the foundations, the article text was processed using the *tm* and *ngram* packages in *R* in order to render the text in lowercase, remove punctuation, and fix spacing issues [@CITE_tm]. The individual words were then reduced to their stems (i.e., *abused* was stemmed to *abus*). The same procedure was applied to the MFD words, and the addition of multiple forms of each concept allowed for the capture of all versions of stemming that might occur given *tm*'s English stemmer function. The source article words were compiled into a dataset where they were matched up with their counterparts in the MFD along with a percentage of their occurrence. Therefore, for each article, the percentage of the number of *harm* (low end) and *care* (high end) related words were calculated and this process was repeated for each of the foundations. This procedure created ten percentages that were included as the dependent variable for the following analyses. 
```{r stem_text, eval=TRUE, include=FALSE}

@@

# Results

@@

```{r exp1-table, results = 'asis', echo = F}
#MFD, mean, sd, mean, sd, t, p, d
tableprint = matrix(NA, ncol = 8, nrow = 5)
colnames(tableprint) = c("Foundation", "M_C", "SD_C", "M_L", "SD_L", "t", "p", "d")

#calculate d
harm_d = d.ind.t(m1 = mean(harm_final_temp$MFDweight[harm_final_temp$lean == "Conservative"], na.rm = T), 
                 m2 = mean(harm_final_temp$MFDweight[harm_final_temp$lean == "Liberal"], na.rm = T),
                 sd1 = sd(harm_final_temp$MFDweight[harm_final_temp$lean == "Conservative"], na.rm = T),
                 sd2 = sd(harm_final_temp$MFDweight[harm_final_temp$lean == "Liberal"], na.rm = T),
                 n1 = length(harm_final_temp$MFDweight[harm_final_temp$lean == "Conservative"]),
                 n2 = length(harm_final_temp$MFDweight[harm_final_temp$lean == "Liberal"]),
                 a = .05)

#put in the numbers
tableprint[1, ] = c("Harm", harm_d$M1, harm_d$sd1, harm_d$M2, harm_d$sd1, 
                    summary(harm_model)$tTable[2,4], summary(harm_model)$tTable[2,5],
                    harm_d$d)

tableprint[ , c(2:6, 8)] = printnum(as.numeric(tableprint[ , c(2:6, 8)]))
tableprint[ , 7] = printp(as.numeric(tableprint[ , 7]))
```
# Discussion

# Experiment 2

Kav stuff here

# Method

@@

Expected material stuff
- we are going to pick liberal and conservative sources from that thing document linked stuff
- list those here:

- pick a specific date range we want to pull articles from 
- list that here: here's when the stuff was happening and so picked two weeks before and after

@@

How you would run the data analysis

@@

# Conclusions

How it turned out
